---
title: "sem vignette with lexdec dataset"
author: "Jason W. Gullifer"
date: '2017-04-04'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{sem vignette with lexdec dataset}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load the required packages
```{r library}
library(languageR)
library(convenience)
library(ggplot2)
library(dplyr)
```

## Load lexdec dataset
```{r lexdec}
data(lexdec)
```

## Data prep
Correct trials only for reaction time analysis. All trials for accuracy analysis. Convert the accuracy column to numeric.
```{r dataprep}
lexdec.rt <- lexdec[lexdec$Correct=="correct",]
lexdec.acc <- lexdec

lexdec.acc$accuracy<-ifelse(lexdec.acc$Correct == "correct",1, 0)
```

## Compute standard error
Use the sem function to compute the mean, standard error of the mean, and 1SEM (68%) confidence intervals
```{r sem}
sem_summary.rt <- sem(data = lexdec.rt, dv = RT, id = Subject, Class, Complex, NativeLanguage)
print(sem_summary.rt)

sem_summary.acc <- sem(data = lexdec.acc, dv = accuracy, id = Subject, Class, Complex,NativeLanguage)
print(sem_summary.acc)
```

## Plotting
Plot the resulting data with 95% confidence intervals (mean $\pm$ 1.96 * sem). You could also set ymin and ymax to upper and lower if you want error bars representing 1 standard error of the mean. 
```{r plot}
ggplot(sem_summary.rt, aes(x = Class, color=NativeLanguage, y = mean_RT, ymin = mean_RT - 1.96 * SEM, ymax = mean_RT + 1.96 * SEM)) + facet_wrap(~Complex) + geom_pointrange(position = position_dodge(.9))

ggplot(sem_summary.acc, aes(x = Class, color=NativeLanguage, y = mean_accuracy, ymin = mean_accuracy - 1.96 * SEM, ymax = mean_accuracy + 1.96 * SEM)) + facet_wrap(~Complex) + geom_pointrange(position = position_dodge(.9))

```

You could also set ymin and ymax to lower and upper if you want error bars representing 1 standard error of the mean. 
```{r plot_1sem}
ggplot(sem_summary.rt, aes(x = Class, color=NativeLanguage, y = mean_RT, ymin = lower, ymax = upper)) + facet_wrap(~Complex) + geom_pointrange(position = position_dodge(.9))

ggplot(sem_summary.acc, aes(x = Class, color=NativeLanguage, y = mean_accuracy, ymin = lower, ymax = upper)) + facet_wrap(~Complex) + geom_pointrange(position = position_dodge(.9))

```
